Nirdizati: A Web-Based Tool for\\ Predictive Process Monitoring

### 2017-07-31 BPM17-demo-paper/paper.tex
camera ready - final version

Nirdizati consists of two components: \textit{Nirdizati Training} and \textit{Nirdizati Runtime} (\figurename~\ref{fig:nirdizati-overall}). Nirdizati Training takes as input a business process event log and produces one or more predictive models, which can then be deployed in Nirdizati Runtime. Once a model is deployed, Nirdizati Runtime listens to a stream of events coming from information systems supporting the process, and produces a stream of predictions. These predictions are then visualized in a continuously updated web dashboard.
%Nirdizati consists of two components: Nirdizati Training and Nirdizati Runtime (Figure~\ref{fig:nirdizati-overall}). Nirdizati Training takes as input a business process event log and produces a predictive model. This model can then be deployed in Nirdizati Runtime. Once a model is deployed, Nirdizati Runtime listens to a stream of events related to a business process, and produces a stream of predictions. These predictions are then visualized in a continuously updated web dashboard.

@@

\section{Nirdizati Runtime} \label{sec:runtime}
Once the predictive models have been created, they are used by the Runtime component to make predictions on ongoing cases.
As input, Nirdizati Runtime takes a stream of events produced by information systems that register the tasks performed in organizations (\figurename~\ref{fig:dfd_0}).
For scalable and fault-tolerant processing, we use the open-source stream processing platform Apache Kafka.
Events belonging to the same process case are collated to make predictions for that case.
A web server communicates with a predictive engine that queries the predictive models obtained by Nirdizati Training.
The results from all predictors are joined and visualized in a dashboard-based interface, which supports several visualization options.

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{img/nirdizati-dataflow}
	\caption{High-level data flow diagram of Nirdizati Runtime.}
	\label{fig:dfd_0}
\end{figure}
%\vspace{-\baselineskip}

@@

\section{Conclusion} \label{sec:conclusion}
Nirdizati is a configurable full-stack web application that supports users in selecting and tuning prediction methods from a list of implemented algorithms and that enables the continuous prediction of various performance indicators at runtime.
The predictions, as well as real-time summary statistics about the process executions, are presented in a dashboard that offers multiple visualization options.

>>>>

Nirdizati consists of two components: \textit{Nirdizati Training} and \textit{Nirdizati Runtime} (\figurename~\ref{fig:nirdizati-overall}). Nirdizati Training takes as input a business process event log and produces one or more predictive models, which can then be deployed in Nirdizati Runtime. Once a model is deployed, Nirdizati Runtime listens to a stream of events coming from an information system supporting the process, and produces a stream of predictions. These predictions are then visualized in a continuously updated web dashboard.
%Nirdizati consists of two components: Nirdizati Training and Nirdizati Runtime (Figure~\ref{fig:nirdizati-overall}). Nirdizati Training takes as input a business process event log and produces a predictive model. This model can then be deployed in Nirdizati Runtime. Once a model is deployed, Nirdizati Runtime listens to a stream of events related to a business process, and produces a stream of predictions. These predictions are then visualized in a continuously updated web dashboard.

@@

\section{Nirdizati Runtime} \label{sec:runtime}
Once the predictive models have been created, they are used by the Runtime component to make predictions on ongoing cases.
Nirdizati Runtime takes a stream of events produced by an information system, transforms it into a stream of predictions, and visualizes those predictions in a web-based dashboard.
The transformation is implemented using the dataflow pipeline in \figurename~\ref{fig:dfd_0}. 
The pipeline is built on top of the open-source Apache Kafka stream processing platform. The ``predictor'' components of the pipeline are the predictive models from Nirdizati Training. The ``topic'' components are network-accessible queues of JSON messages with publisher/subscriber support. This allows the computationally intense work of the predictors to be distributed across a cluster of networked computers, providing scalability and fault-tolerance.
The ``collator'' component accumulates the sequence of events-to-date for each case, such that the prediction is a stateless function of the trained predictive model and of the case history.  This statelessness is what allows the predictors to be freely duplicated and distributed.  The ``joiner'' component composes the original events with the various predictions, ready for display on the dashboard.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.9\textwidth]{img/nirdizati-dataflow}
	\caption{High-level data flow diagram of Nirdizati Runtime.}
	\label{fig:dfd_0}
\end{figure}
%\vspace{-\baselineskip}

@@

\section{Conclusion} \label{sec:conclusion}
Nirdizati is a configurable full-stack web application that supports users in selecting and tuning prediction methods from a list of implemented algorithms and that enables the continuous prediction of various performance indicators at runtime.
The predictions are presented in a dashboard that offers multiple visualization options.
